### 2022-09-28 code/3_analysis/3_analysis.Rmd
removed thesis sections

affiliation:
  - id            : "1"
    institution   : "Symbolic Systems Program"
  - id            : "2"
    institution   : "Stanford University"

authornote: |
    An honors thesis submitted to the program of Symbolic Systems of Stanford University in partial fulfillment of the requirements for the degree in Symbolic Systems. 
    Honors Student: Khuyen Le. Honors Advisor: Mike Frank. Second Reader: Alex Carstensen

@@

\newpage
To the Directors of the Program on Symbolic Systems:

I certify that I have read the thesis of Khuyen Le in its final form for submission and have found it to be satisfactory for the degree of Bachelor of Science with Honors.

Signed electronically

06/04/2021

Michael C. Frank

Department of Psychology

To the Directors of the Program on Symbolic Systems:

I certify that I have read the thesis of Khuyen Le in its final form for submission and have found it to be satisfactory for the degree of Bachelor of Science with Honors.

Signed electronically

06/04/2021

Alex Carstensen

Department of Psychology

@@

# Results
```{r combine corpus and behavior data, include = F}
source("../2_combine/2_combine.Rmd")
```

>>>>

affiliation:
  - id            : "1"
    institution   : "Psychology Department"
  - id            : "2"
    institution   : "University of California, San Diego"

@@

@@

# Results
```{r combine corpus and behavior data, include = F}
#source("../2_combine/2_combine.Rmd")
df <- read.csv("../../data/data_USCNVN_ENZHVI.csv")
```
